Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-09 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Adding an example...

>>>>

For example, we can extend one of the fragments of valid probability
measures~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy} to a QIVPM~$\bar{\mu}_{3}$:
$\bar{\mu}_{3}(\proj{0})=\left[0.5,0.5\right]$, $\bar{\mu}_{3}(\proj{1})=\left[0.5,0.5\right]$,
and $\bar{\mu}_{3}(\proj{2})=\left[0,0\right]$. For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
the Born rule probability~$\mu_{\rho}^{\mathrm{B}}$ of any state~$\rho$
consistent with $\bar{\mu}_{3}$ on $\proj{0}$, $\proj{1}$, and
$\proj{2}$ must be $\mu_{1}$. Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
which is an interval, but not between $0$ and $1$ because it is
not a probability of an event.
